Face Recognition: Too Bias, or Not Too Bias?

### 2020-07-09 sections/relatedworks.tex
camera-ready

\section{Background Information}
    \subsection{Bias in \gls{ml}}
        The progress and commercial value of \gls{ml} is exciting; however, the trust of society in \gls{ml} will take time to build due to inherent biases. The exact definitions and implications of bias vary between sources, as do its sources and types. A common theme is that bias hinders performance ratings in ways that skew to a particular sub-population-- the source varies, whether from humans~\cite{windmann1998subconscious}, data and label types~\cite{tommasi2017deeper}, \gls{ml} models~\cite{amini2019uncovering, kim2019learning}, or evaluation protocols~\cite{stock2018convnets}. For instance, a vehicle-detection model might miss cars if training data was mostly trucks. In practice, many \gls{ml} systems learn on biased data, which could be detrimental for society.

    \subsection{Bias in \gls{fr}}
        Problems of bias in \gls{fr} have been driven by different motivations; therefore, solutions have been posed for different matters. Instances can be in problems of data augmentation~\cite{yin2019feature}, one-shot learning~\cite{ding2018one}, demographic parity and fairness with priority on privacy~\cite{huang2018generative}, domain adaptation~\cite{wang2018racial}, differences in face-based attributes across demographics~\cite{wang2018they}, and even data exploration~\cite{muthukumar2019}. Yin~\etal proposed to augment the feature space of underrepresented classes using other classes with a diverse collection of samples to encourage distributions of underrepresented classes to more closely resemble that of the others~\cite{yin2019feature}. Similarly, others formulated the imbalanced class problem as one-shot learning, where a \gls{gan} was trained to generate face features to augment classes with fewer samples~\cite{ding2018one}. \gls{gapf} was proposed to create fair representations of the data in a quantifiable way, allowing for the finding of a de-correlation scheme from the data without access to its statistics~\cite{huang2018generative}. Wang~\etal defined subgroups at a finer-level (\ie Chinese, Japanese, Korean), and determined the familiarity of faces inter-subgroup~\cite{wang2018they}. Genders have also been used to make subgroups (\eg for analysis of gender-based face encodings~\cite{muthukumar2019}). Most recently,~\cite{wang2018racial} proposed to adapt domains to bridge the bias gap by knowledge transfer, which was supported by a novel data collection, \gls{rfw}. The release of \gls{rfw} occurred after \gls{bfw} was built - although similar in terms of demographics, \gls{rfw} uses faces from MSCeleb~\cite{guo2016ms} for testing, and assumes CASIA-Face~\cite{yi2014learning} and VGG2~\cite{Cao18} were used to train. In contrast, our \gls{bfw} assumes VGG2 as the test set. 
        % As shown in \cite{wang2018racial}, MSCeleb is highly imbalanced, primarily consisting of images of white individuals. 
        % For this, we expect bias from data, for this is the training set. 
        Furthermore, \gls{bfw} balances gender and race: \gls{rfw} splits subgroups by gender and race, while \gls{bfw} has gender, race, or both). 
        % Thus, \gls{rfw} and \gls{bfw} complement one another. % - both add demographic for subjects with faces in renowned, large-scale \gls{fr} datasets.

Most similar to us is~\cite{das2018, demogPairs, lopez2019dataset, srinivas2019face} - each were motivated by insufficient paired data for studying bias in \gls{fr}. Then, problems were addressed using labeled data from existing image collections. Specifically, Hupont~\etal curated a set of faces based on racial demographics (\ie \gls{a}, \gls{b}, and \gls{w}) called \gls{dp}~\cite{demogPairs}, while~\cite{srinivas2019face} honed in on adults versus children called \gls{itwcc}. Like the proposed \gls{bfw}, both were built by sampling existing databases, but with the addition of tags for the respective subgroups of interest. Aside from the additional data of \gls{bfw} (\ie added an additional subgroup \gls{i}, along with additional subjects with more faces for all subgroups), we also further split subgroups by gender. Furthermore, we focus on the problem of facial verification and the different levels of sensitivity in cosine similarity scores per subgroup.

@@

        \centering
        \caption{\small{\textbf{\gls{bfw} compared to related datasets.} Our \gls{bfw} is balanced across ID, gender, and ethnicity (Table~\ref{tab:ethnic-splits}). Compared with \gls{dp}, \gls{bfw} provides more samples per subject and subgroups per set, while only using a single resource, VGG2. \gls{rfw}, on the other hand, supports a different task (\ie domain adaptation), and focuses on race-distribution, but not the distribution of identities.}}
        \scriptsize
        \begin{tabular}{rccccccc}%x{10mm}x{3mm}x{10mm}x{8mm}}%\toprule

            \multicolumn{2}{c}{Database} & \multicolumn{3}{c}{Number of}& \multicolumn{3}{c}{Balanced Labels}\\
            \cmidrule(lr){1-2}	\cmidrule(lr){3-5} \cmidrule(lr){6-8}
            Name & Source Data & Faces &  IDs & Subgroups & ID & Ethnicity & Gender\\\midrule
            \gls{dp}~\cite{demogPairs}     & CASIA-W~\cite{yi2014learning}, VGG~\cite{schroff2015facenet} \&VGG2~\cite{Cao18} & 10,800& 600 & 6 &\checkc& \checkc &\checkc \\
            \gls{rfw}~\cite{wang2018racial}     &  MS-Celeb-1M &$\approx$80,000&$\approx$12,000& 4 & \xmark & \checkc &\xmark \\
            \gls{bfw} (ours) & VGG2 & 20,000 & 800 &8 & \checkc & \checkc &\checkc \\\bottomrule
        \end{tabular}
        \label{tab:compared}
%            \vspace{-5mm}
    \end{table*}

\subsection{Human bias in \gls{ml}}
Bias is not unique to \gls{ml} - humans are also susceptible to a perceived bias. In fact, biases exist across race, gender, and even age~\cite{10.1007/978-3-030-13469-3_68, bar2006, meissner2001, nicholls2018}. Wang~\etal showed machines surpass human performance in discriminating between Japanese, Chinese, or Korean faces by nearly 150\%~\cite{wang2018they}, as humans just pass random (\ie 38.89\% accuracy).

We expect human bias to skew to their own genders and races. For this, we measure the human perception with face pairs of different subgroups (Section~\ref{subsec:human-assessment}). The results concur with~\cite{wang2018they}, as we also recorded overall averages below random ($<$50\%). %The details on settings and number of submissions per demographics are discussed in Section~\ref{}.

>>>>

\section{Background Information}
    \subsection{Bias in \gls{ml}}
        The progress and commercial value of \gls{ml} are exciting. However, due to inherent biases in ML, society is not readily able to trust completely in its widespread use. The exact definitions and implications of bias vary between sources, as do its causes and types. A common theme is that bias hinders performance ratings in ways that skew to a particular sub-population. In essence, the source varies, whether from humans~\cite{windmann1998subconscious}, data or label types~\cite{tommasi2017deeper}, \gls{ml} models~\cite{amini2019uncovering, kim2019learning}, or evaluation protocols~\cite{stock2018convnets}. For instance, a vehicle-detection model might miss cars if training data were mostly trucks. In practice, many \gls{ml} systems learn biased data, which could be detrimental to society.

    \subsection{Bias in \gls{fr}}
        Different motivations have driven problems of bias in \gls{fr}. Instances can be in issues of data augmentation~\cite{yin2019feature}, one-shot learning~\cite{ding2018one}, demographic parity and fairness with priority on privacy~\cite{huang2018generative}, domain adaptation~\cite{wang2018racial}, differences in face-based attributes across demographics~\cite{wang2018they}, data exploration~\cite{muthukumar2019}, and even characterizing different commercial systems~\cite{buolamwini2018gender}.

        Yin~\etal proposed to augment the feature space of underrepresented classes using different classes with a diverse collection of samples~\cite{yin2019feature}. This was to encourage distributions of underrepresented classes to resemble the others more closely. Similarly, others formulated the imbalanced class problem as one-shot learning, where a \gls{gan} was trained to generate face features to augment classes with fewer samples~\cite{ding2018one}. \gls{gapf} was proposed to create fair representations of the data in a quantifiable way, allowing for the finding of a de-correlation scheme from the data without access to its statistics~\cite{huang2018generative}. Wang~\etal defined subgroups at a finer level (\ie Chinese, Japanese, Korean), and determined the familiarity of faces inter-subgroup~\cite{wang2018they}. Genders have also been used to make subgroups (\eg for analysis of gender-based face encodings~\cite{muthukumar2019}). Most recently,~\cite{wang2018racial} proposed to adapt domains to bridge the bias gap by knowledge transfer, which was supported by a novel data collection, \gls{rfw}. The release of \gls{rfw} occurred after \gls{bfw} was built - although similar in terms of demographics, \gls{rfw} uses faces from MSCeleb~\cite{guo2016ms} for testing, and assumes CASIA-Face~\cite{yi2014learning} and VGG2~\cite{Cao18} were used to train. In contrast, our \gls{bfw} assumes VGG2 as the test set. 
        % As shown in \cite{wang2018racial}, MSCeleb is highly imbalanced, primarily consisting of images of white individuals. 
        % For this, we expect bias from data, for this is the training set. 
        Furthermore, \gls{bfw} balance subgroups: \gls{rfw} splits subgroups by gender and race, while \gls{bfw} has gender, race, or both). 
        % Thus, \gls{rfw} and \gls{bfw} complement one another. % - both add demographic for subjects with faces in renowned, large-scale \gls{fr} datasets.

Most similar to us is~\cite{das2018, demogPairs, lopez2019dataset, srinivas2019face} - each was motivated by insufficient paired data for studying bias in \gls{fr}. Then, problems were addressed using labeled data from existing image collections. Uniquely, Hupont~\etal curated a set of faces based on racial demographics (\ie \gls{a}, \gls{b}, and \gls{w}) called \gls{dp}~\cite{demogPairs}. In contrast,~\cite{srinivas2019face} honed in on adults versus children called \gls{itwcc}. Like the proposed \gls{bfw}, both were built by sampling existing databases, but with the addition of tags for the respective subgroups of interest. Aside from the additional data of \gls{bfw} (\ie added subgroup \gls{i}, along with other subjects with more faces for all subgroups), we also further split subgroups by gender. Furthermore, we focus on the problem of facial verification and the different levels of sensitivity in cosine similarity scores per subgroup.

@@

        \centering
        \caption{\small{\textbf{\gls{bfw} and related datasets.} \gls{bfw} is balanced across ID, gender, and ethnicity (Table~\ref{tab:ethnic-splits}). Compared with \gls{dp}, \gls{bfw} provides more samples per subject and subgroups per set, while using a single resource, VGG2. \gls{rfw}, on the other hand, supports domain adaptation, and focuses on race-distribution - not the distribution of identities.}}
        \scriptsize
        \begin{tabular}{rccccccc}%x{10mm}x{3mm}x{10mm}x{8mm}}%\toprule

            \multicolumn{2}{c}{Database} & \multicolumn{3}{c}{Number of}& \multicolumn{3}{c}{Balanced Labels}\\
            \cmidrule(lr){1-2}	\cmidrule(lr){3-5} \cmidrule(lr){6-8}
            Name & Source Data & Faces &  IDs & Subgroups & ID & Ethnicity & Gender\\\midrule
            \gls{dp}~\cite{demogPairs}     & CASIA-W~\cite{yi2014learning}, VGG~\cite{schroff2015facenet} \&VGG2~\cite{Cao18} & 10,800& 600 & 6 &\checkc& \checkc &\checkc \\
            \gls{rfw}~\cite{wang2018racial}     &  MS-Celeb-1M &$\approx$80,000&$\approx$12,000& 4 & \xmark & \checkc &\xmark \\
            \gls{bfw} (ours) & VGG2 & 20,000 & 800 &8 & \checkc & \checkc &\checkc \\\bottomrule
        \end{tabular}
        \label{tab:compared}
            \vspace{-4mm}
    \end{table*}

\subsection{Human bias in \gls{ml}}
Bias is not unique to \gls{ml} - humans are also susceptible to a perceived bias. Biases exist across race, gender, and even age~\cite{10.1007/978-3-030-13469-3_68, bar2006, meissner2001, nicholls2018}. Wang~\etal showed machines surpass human performance in discriminating between Japanese, Chinese, or Korean faces by nearly 150\%~\cite{wang2018they}, as humans just pass random (\ie 38.89\% accuracy).

We expect the human bias to skew to their genders and races. For this, we measure human perception with face pairs of different subgroups (Section~\ref{subsec:human-assessment}). The results concur with~\cite{wang2018they}, as we also recorded overall averages below random ($<$50\%). %The details on settings and number of submissions per demographics are discussed in Section~\ref{}.

### 2020-07-09 sections/section3.tex
camera-ready

\section{The BFW Benchmark and Dataset}

We now discuss the \gls{bfw} dataset (\ie collection and preparation), along with the evaluation protocols. We conclude this section by reviewing the settings used to survey bias in humans.

@@

\vspace{1mm}
\noindent\textbf{Compiling subject list.} 
Subjects were sampled from VGG2~\cite{Cao18} - unlike others built from multiple sources, \gls{bfw} has fewer potential conflicts in train and test overlap with existing models. To find candidates for the different subgroups, we first parsed the list of names using a pre-trained ethnicity model~\cite{ambekar2009name}. This was then further refined by processing faces using ethnicity~\cite{fu2014learning} and gender~\cite{levi2015age} classifiers. This resulted in hundreds of candidates per subgroup, which allowed us to manually filter 100 subjects per the 8 subgroups.

\vspace{1mm}
\noindent\textbf{Detecting faces.} Faces were detected using MTCNN~\cite{zhang2016joint}.\footnote{\href{https://github.com/polarisZhao/mtcnn-pytorch}{https://github.com/polarisZhao/mtcnn-pytorch}} Then, faces were assigned to one of two sets. Faces within detected bounding box (BB) regions extended out 130\% in each direction, with zero-padding as the boundary condition made-up one set. The second set were faces aligned and cropped for Sphereface~\cite{liu2017sphereface} (see the next step). Also, coordinates of the BB and the five landmarks from \gls{mtcnn} were stored as part of the static, raw data. For samples with multiple face detections, we used the BB area times the confidence score of the \gls{mtcnn} to determine the face most likely to be the subject of interest, with the others set aside and labeled \textit{miss-detection}.

\vspace{1mm}
\noindent\textbf{Validating labels.} 
Faces of \gls{bfw} were encoded using the original implementation of the \gls{soa} Sphereface~\cite{liu2017sphereface}. For this, each face was aligned to predefined eye locations via an affine transformation. Then, faces were fed through the \gls{cnn} twice (\ie the original and horizontally flipped), with two features fused by average pooling (\ie 512 D). A matrix of cosine similarity scores was then generated for each subject and removed samples (\ie rows) with median scores below threshold $\theta=0.2$ (set manually). Mathematically, the $n^{th}$ sample for the $j^{th}$ subject with $N_j$ faces was removed if the ordinal rank of its score $n = \frac{P\times N}{100}\geq\theta$, where $P=50$. In other words, the median (\ie 50 percentile) of all scores for a face with respect to all of faces for the respective subject must pass a threshold of $\theta=0.2$; else, the face is dropped. This allowed us to quickly prune \gls{fp} face detections. Following~\cite{robinson2016families, robinson2018visual}, we built a JAVA tool to visually validate the remaining faces. For this, the faces were ordered by decreasing confidence, with confidence set as the average score, and then displayed as image icons on top toggling buttons arranged as a grid in a sliding pane window. Labeling then consisted of going subject-by-subject and flagging faces of \emph{imposters}.

\begin{figure}[!t] 
	\centering    
 \glsunset{fpr}
  \glsunset{fnr}
	\includegraphics[width=.9\linewidth]{figures/detcurve-improved.pdf}
		\caption{\small{\textbf{\gls{det} curves.} \emph{Top-left}: per gender. \emph{Top-right}: per ethnicity. \emph{Bottom}: per subgroup (\ie combined). Dashed line shows about 2$\times$ difference in \gls{fpr} for the same threshold $\theta_{const}$. \gls{fnr} is the match error count (closer to the bottom is better).}}
		\glsreset{det}\glsreset{fpr}
\label{fig:detcurves} 
\end{figure} 
%\vspace{1mm}
\noindent\textbf{Sampling faces and creating folds.} We created lists of pairs in five-folds with subjects split evenly per subject and without overlap across folds. Furthermore, a balance in the number of faces per subgroup was obtained by sampling twenty-five faces at random from each. Next, we generated a list of all the face pairs per subject, resulting in $\sum_{l=1}^{L}\sum_{k=1}^{K_d} {N_k \choose 2}$ positive pairs, where the number of faces of all $K_l$ subjects $N_k=25$  for each of the $L$ subgroups (Table~\ref{tab:ethnic-splits}). Next, we assigned subjects to a fold. To preserve balance across folds, we sorted subjects by the number of pairs and then started assigning to alternating folds from the one with the most samples. Note, this left no overlap in identity between folds. Later, a negative set from samples within the same subgroup randomly matched until the count met that of the positive. Finally, we doubled the number with negative pairs from across subgroups but in the same fold.

\begin{figure}[t!] 
	\glsunset{fpr}
% 	\glsunset{sdm}
	\centering
	\centering
	\includegraphics[width=1\linewidth]{figures/violinplots.pdf}
		\caption{\small{\textbf{\Gls{sdm} across subgroups.} Scores of \emph{imposters} have medians around 0.3 but with variations in upper percentiles; \emph{genuine} pairs vary in mean and spread (\eg \gls{af} has more area of overlap). A threshold varying across different subgroups yields a constant \gls{fpr}.}} \label{fig:detection-model} 
% 		\glsreset{sdm}
\end{figure}

% \vspace{-5pt}
\subsection{Problem formulation}\label{subsec:pf} 
% \gls{lfw}~\cite{LFWTech}, a commonly used benchmark for ~\gls{fr}, reserves specific train-test face-pair lists. 
\Gls{fv} is the special case of the two-class (\ie boolean) classification. Hence, pairs are labeled as the ``same'' or ``different'' \textit{genuine} pairs (\ie \textit{match}) or \textit{imposter} (\ie \textit{mismatch}), respectively. This formulation (\ie \gls{fv}) is highly practical for applications like access control, re-identification, and surveillance. Typically, training a separate model for each unique subject is infeasible. Firstly, the computational costs compound as the number of subjects increase.  Secondly, such a scheme would require model retraining each time a new person is added. Instead, we train models to encode facial images in a feature space that captures the uniqueness of a face, to then determine the outcome based on the output of a scoring (or distance) function. Formally put:
\begin{equation}\label{eg:matcher}
    f_{boolean}(\vec{x}_i, \vec{x}_j) = d(\vec{x}_i, \vec{x}_j) \leq \theta,
\end{equation}

@@

\begin{figure}[t!]
	\centering    
	\includegraphics[width=.75\linewidth]{figures/confusion.pdf}
		\caption{\small{\textbf{Confusion matrix.} Error (Rank 1, \%) for all faces of \gls{bfw} vs. all others. Error concentrates intra-subgroup - consistent with the \gls{sdm} (Fig.~\ref{fig:detection-model}), as \gls{af} performs the worst, mostly confused by \gls{af}. Although race/ethnicity are challenging to define, this shows the subgroups are meaningful for \gls{fr}.}}
		\label{fig:confusion} 
%		    \vspace{-6mm}
\end{figure}

@@

Samples were collected from individuals recruited from multiple sources (\eg social media, email lists, and family/friends) - a total of 120 participants were sampled at random from all the submissions that were (1) complete and (2) done by a W or C participant. Specifically, there were 60 W and 60 C, both with \gls{m} and \gls{f} split evenly. A total of 50 face pairs of non-famous ``look-alikes'' were collected from the internet, with 20 ({\emph WA}) and 20 ({\emph C}) pairs with, again, \gls{m} and \gls{f} split evenly. The other 10 pairs were of a different demographic (\eg Hispanic/ Latino, Japanese, African). The survey was created, distributed, and recorded via \href{https://paperform.co}{PaperForm}. It is important to note that participants were only aware of the task (\ie to verify whether or not a face-pair was a \emph{match} or \emph{non-match}, but with no knowledge of it being a study on bias).

>>>>

\section{The BFW Benchmark and Dataset}
We now discuss the acquisition of \gls{bfw}, protocols, and settings used to survey bias in humans.

@@

\vspace{.5mm}
\noindent\textbf{Compiling subject list.} 
Subjects were sampled from VGG2~\cite{Cao18} - unlike others built from multiple sources, \gls{bfw} has fewer potential conflicts in train and test overlap with existing models. To find candidates for the different subgroups, we first parsed the list of names using a pre-trained ethnicity model~\cite{ambekar2009name}. This was then further refined by processing faces using ethnicity~\cite{fu2014learning} and gender~\cite{levi2015age} classifiers. This resulted in hundreds of candidates per subgroup, which allowed us to manually filter 100 subjects per the 8 subgroups.

\vspace{.5mm}
\noindent\textbf{Detecting faces.} Faces were detected using MTCNN~\cite{zhang2016joint}.\footnote{\href{https://github.com/polarisZhao/mtcnn-pytorch}{https://github.com/polarisZhao/mtcnn-pytorch}} Then, faces were assigned to one of two sets. Faces within detected bounding box (BB) regions extended out 130\% in each direction, with zero-padding as the boundary condition made-up one set. The second set were faces aligned and cropped for Sphereface~\cite{liu2017sphereface} (see the next step). Also, coordinates of the BB and the five landmarks from \gls{mtcnn} were stored as part of the static, raw data. For samples with multiple face detections, we used the BB area times the confidence score of the \gls{mtcnn} to determine the face most likely to be the subject of interest, with the others set aside and labeled \textit{miss-detection}.

\vspace{.5mm}
\noindent\textbf{Validating labels.} 
Faces of \gls{bfw} were encoded using the original implementation of the \gls{soa} Sphereface~\cite{liu2017sphereface}. For this, each face was aligned to predefined eye locations via an affine transformation. Then, faces were fed through the \gls{cnn} twice (\ie the original and horizontally flipped), with two features fused by average pooling (\ie 512 D). A matrix of cosine similarity scores was then generated for each subject and removed samples (\ie rows) with median scores below threshold $\theta=0.2$ (set manually). Mathematically, the $n^{th}$ sample for the $j^{th}$ subject with $N_j$ faces was removed if the ordinal rank of its score $n = \frac{P\times N}{100}\geq\theta$, where $P=50$. In other words, the median (\ie 50 percentile) of all scores for a face with respect to all of faces for the respective subject must pass a threshold of $\theta=0.2$; else, the face is dropped. This allowed us to quickly prune \gls{fp} face detections. Following~\cite{robinson2016families, robinson2018visual}, we built a JAVA tool to visually validate the remaining faces. For this, the faces were ordered by decreasing confidence, with confidence set as the average score, and then displayed as image icons on top toggling buttons arranged as a grid in a sliding pane window. Labeling then consisted of going subject-by-subject and flagging faces of \emph{imposters}.

\begin{figure}[!t] 
	\centering    
 \glsunset{fpr}
  \glsunset{fnr}
	\includegraphics[width=.83\linewidth]{figures/detcurve-improved.pdf}
		\caption{\small{\textbf{\gls{det} curves.} \emph{Top-left}: per gender. \emph{Top-right}: per ethnicity. \emph{Bottom}: per subgroup (\ie combined). Dashed line shows about 2$\times$ difference in \gls{fpr} for the same threshold $\theta_{const}$. \gls{fnr} is the match error count (closer to the bottom is better).}}
		\glsreset{det}\glsreset{fpr}
\label{fig:detcurves} 
 \vspace{-4mm}
\end{figure} 
%\vspace{1mm}
\noindent\textbf{Sampling faces and creating folds.} We created lists of pairs in five-folds with subjects split evenly per person and without overlap across folds. Furthermore, a balance in the number of faces per subgroup was obtained by sampling twenty-five faces at random from each. Next, we generated a list of all the face pairs per subject, resulting in $\sum_{l=1}^{L}\sum_{k=1}^{K_d} {N_k \choose 2}$ positive pairs, where the number of faces of all $K_l$ subjects $N_k=25$  for each of the $L$ subgroups (Table~\ref{tab:ethnic-splits}). Next, we assigned subjects to a fold. To preserve balance across folds, we sorted subjects by the number of pairs and then started assigning to alternating folds from the one with the most samples. Note, this left no overlap in identity between folds. Later, a negative set from samples within the same subgroup randomly matched until the count met that of the positive. Finally, we doubled the number with negative pairs from across subgroups but in the same fold.

\begin{figure}[t!] 
	\glsunset{fpr}
% 	\glsunset{sdm}
	\centering
	\centering
	\includegraphics[width=1\linewidth]{figures/violinplots.pdf}
		\caption{\small{\textbf{\Gls{sdm} across subgroups.} Scores of \emph{imposters} have medians around 0.3 but with variations in upper percentiles; \emph{genuine} pairs vary in mean and spread (\eg \gls{af} has more area of overlap). A threshold varying across different subgroups yields a constant \gls{fpr}.}} \label{fig:detection-model} 
% 		\glsreset{sdm}
	    \vspace{-4mm}
\end{figure}

% \vspace{-5pt}
\subsection{Problem formulation}\label{subsec:pf} 
% \gls{lfw}~\cite{LFWTech}, a commonly used benchmark for ~\gls{fr}, reserves specific train-test face-pair lists. 
\Gls{fv} is the special case of the two-class (\ie boolean) classification. Hence, pairs are labeled as the ``same'' or ``different'' \textit{genuine} pairs (\ie \textit{match}) or \textit{imposter} (\ie \textit{mismatch}), respectively. This formulation (\ie \gls{fv}) is highly practical for applications like access control, re-identification, and surveillance. Typically, training a separate model for each unique subject is unfeasible. Firstly, the computational costs compound as the number of subjects increase.  Secondly, such a scheme would require model retraining each time a new person is added. Instead, we train models to encode facial images in a feature space that captures the uniqueness of a face, to then determine the outcome based on the output of a scoring (or distance) function. Formally put:
\begin{equation}\label{eg:matcher}
    f_{boolean}(\vec{x}_i, \vec{x}_j) = d(\vec{x}_i, \vec{x}_j) \leq \theta,
\end{equation}

@@

\begin{figure}[t!]
	\centering    
	\includegraphics[width=.65\linewidth]{figures/confusion.pdf}
		\caption{\small{\textbf{Confusion matrix.} Error (Rank 1, \%) for all \gls{bfw} faces versus all others. Errors concentrate intra-subgroup - consistent with the \gls{sdm} (Fig.~\ref{fig:detection-model}). Although subgroups are challenging to define, this shows the ones chosen are meaningful for \gls{fr}.}}
		\label{fig:confusion} 
		  %  \vspace{-3mm}
\end{figure}

@@

Samples were collected from individuals recruited from multiple sources (\eg social media, email lists, family, and friends) - a total of 120 participants were sampled at random from all submissions that were completed and done by a W or C participant. Specifically, there were 60 W and 60 C, both with \gls{m} and \gls{f} split evenly. A total of 50 face pairs of non-famous ``look-alikes'' were collected from the internet, with 20 ({\emph WA}) and 20 ({\emph C}) pairs with, again, \gls{m} and \gls{f} split evenly. The other 10 were of a different demographic (\eg Hispanic/ Latino, Japanese, African). The survey was created, distributed, and recorded via \emph{\href{https://paperform.co}{PaperForm}}. It is important to note that participants were only aware of the task (\ie to verify whether or not a face-pair was a \emph{match} or \emph{non-match}, but with no knowledge of it being a study on the bias).
